### 2023-04-02 outputs/paper.qmd
Initial commit

---
title: "Fast Fashion's Production Rate is Observedly Unsustainable: Why and How did we get here?"
author: "Jayden Jung"
thanks: "Code and data are available at: https://github.com/jj-andj/fast-fashion-analysis"
date: "April 21, 2023"
date-format: long
format: 
  pdf: 
    documentclass: article
    geometry: margin = 1in
    abstract: "An abstract is included and appropriately pitched to a non-specialist audience. The abstract answers: 1) what was done, 2) what was found, and 3) why this matters (all at a high level). Likely four sentences. Abstract must make clear what we learn about the world because of this paper."
output: 
  bookdown::pdf_document2
toc: false
fig_caption: yes
nocite: '@*'
bibliography: references.bib
---

# Introduction

> "Fast fashion isn't free. Someone, somewhere is paying."
>
> --- Lucy Siegle, Journalist and Producer of *The True Cost*, 2015.

1\) broader context to motivate; 2) some detail about what the paper is about; 3) a clear gap that needs to be filled; 4) what was done; 5) what was found; 6) why it is important; 7) the structure of the paper. A reader should be able to read only the introduction and know what was done, why, and what was found.

Estimand

# Data

Lorem

# Results

Lorem

# Discussion

## Findings

Lorem

## Why did we get here? Exploring culture-based roots of Fast Fashion

Lorem

## At what cost? Reviewing the ramifications of Fast Fashion

Lorem

## Defining Solution Spaces

Lorem

## Future Research

Lorem

## Limitations

Lorem

\clearpage

# References {.unnumbered}

### 2023-04-02 scripts/00-simulate.R

@@ -1,0 +1,53 @@
+#### Preamble ####
+# Purpose: Simulate data on 2 ecommerce companies' products on 2 separate dates
+# Author: Jayden Jung
+# Email: jayden.jung@mail.utoronto.ca
+# Date: Apr 21 2023
+# Prerequisites: None
+
+### Set Up ###
+
+library(readr)
+library(tidyverse)
+
+#### Simulate ####
+set.seed(309)
+
+# Random string generator for product names https://stackoverflow.com/questions/42734547/generating-random-strings
+randostring <- function(n = 5000) {
+  a <- do.call(paste0, replicate(5, sample(LETTERS, n, TRUE), FALSE))
+  paste0(a, sprintf("%04d", sample(9999, n, TRUE)), sample(LETTERS, n, TRUE))
+}
+
+# "Before" state of products of both stores
+store1date1 <- 
+  tibble(
+    products = randostring(20))
+
+store2date1 <- 
+  tibble(
+    products = randostring(24))
+
+# "After" state of products of both stores
+store1date2 <- 
+  store1date1 %>% 
+  add_row(products = randostring(1))
+  
+# "Fast fashion" company shows many products being retired/replaced and more products added
+store2date2 <-
+  store2date1[-c(1,2,4,6,9,13,19,20),] %>% 
+  add_row(products = randostring(12))
+
+# See how simulated data looks
+store1date1
+store1date2
+
+store2date1
+store2date2
+
+# Download simulated data
+write_csv(store1date1, "inputs/0-simulation/store1date1.csv")
+write_csv(store1date2, "inputs/0-simulation/store1date2.csv")
+
+write_csv(store2date1, "inputs/0-simulation/store2date1.csv")
+write_csv(store2date2, "inputs/0-simulation/store2date2.csv")

### 2023-04-02 scripts/01-test.R

@@ -1,0 +1,26 @@
+#### Preamble ####
+# Purpose: Test simulated data of ecommerce site products
+# Author: Jayden Jung
+# Email: jayden.jung@mail.utoronto.ca
+# Date: Apr 21 2023
+# Prerequisites: Have run 00-simulate.R and have the relevant csvs saved
+
+# Read in simulated data
+store1date1 <- read_csv(here::here("inputs/0-simulation/store1date1.csv"),
+                        show_col_types = FALSE)
+store1date2 <- read_csv(here::here("inputs/0-simulation/store1date2.csv"),
+                        show_col_types = FALSE)
+
+### Testing ###
+
+# Test class to be correct type (character)
+class(store1date1$products) == "character"
+
+# Ensure that there is only one column (products)
+length(store1date1) == 1
+
+# Ensure there are no duplicate products
+duplicated(store1date1) == FALSE
+
+# Make sure that the two versions are not entirely equal
+isTRUE(all.equal(store1date1,store1date2)) == FALSE

### 2023-04-02 scripts/02-gather_data.R

@@ -1,0 +1,70 @@
+#### Preamble ####
+# Purpose: Gather names of all products of KOTN and Zaful on two separate dates
+# Author: Jayden Jung
+# Email: jayden.jung@mail.utoronto.ca
+# Date: Apr 21 2023
+# Prerequisites: Use Web Scraper chrome extension for scraping KOTN data
+
+# Set up
+library(xml2)
+library(rvest)   
+library(tidyverse)
+library(dplyr)
+library(httr)
+
+### KOTN Products ###
+# Collected with chrome extension: https://www.webscraper.io/ 
+# with selector set as: .products_grid__SIeIQ div.ProductCard_innerContainer__Gp3qg:nth-of-type(2) h2
+# Collected dates: April 2nd & April 11th
+
+### Zaful Products (April 2nd & April 11th) ###
+#Set Headers
+headers <- c("User-Agent" = "Mozilla/5.0 (Windows NT 10.0; Win64; x64) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/58.0.3029.110 Safari/537.36")
+
+## First date
+#Create empty data frame
+z_products <- data.frame()
+
+#Loop through all product pages (sequence max set by what is seen on site) 
+for(page_result in seq(from = 1, to = 122, by = 1)) {
+  url = paste0("https://www.zaful.com/clothes-e_1/g_", 
+              page_result, ".html")
+  raw_page <- GET(url, add_headers(headers))
+  html <- read_html(raw_page)
+  
+  # Scrape all product names on given page
+  products <- html %>% html_elements(".js_list_title") %>% html_text()
+  
+  # Add each page's products to data frame
+  z_products <- rbind(z_products, data.frame(products=products))
+  
+  # Print page number to track progress, not necessary
+  print(paste("Page:", page_result))
+}
+
+#Write csv of product list
+write_csv(z_products, "inputs/zafulapril2.csv")
+
+## Second date
+#Create empty data frame
+z_products2 <- data.frame()
+
+#Loop through all product pages (sequence max set by what is seen on site) 
+for(page_result in seq(from = 1, to = 122, by = 1)) {
+  url = paste0("https://www.zaful.com/clothes-e_1/g_", 
+               page_result, ".html")
+  raw_page <- GET(url, add_headers(headers))
+  html <- read_html(raw_page)
+  
+  # Scrape all product names on given page
+  products <- html %>% html_elements(".js_list_title") %>% html_text()
+  
[…]

### 2023-04-02 outputs/paper.qmd
Editing title

@@
 ---
-title: "Fast Fashion's Production Rate is Observedly Unsustainable: Why and How did we get here?"
+title: "Fast Fashion's Rapid Rate of Overoduction is Observedly Unsustainable, & Unethical: Why and How did we get here?"
 author: "Jayden Jung"

### 2023-04-04 outputs/paper.qmd
Writing paper

--- 2023-04-02 outputs/paper.qmd
@@
 ---
-title: "Fast Fashion's Production Rate is Observedly Unsustainable: Why and How did we get here?"
+title: "Fast Fashion's Rapid Rate of Overproduction is Observedly Unsustainable & Unethical: Why and How did we get here?"
 author: "Jayden Jung"
@@
     geometry: margin = 1in
-    abstract: "An abstract is included and appropriately pitched to a non-specialist audience.
-The abstract answers: 1) what was done, 2) what was found, and 3) why this matters (all at a high level).
-Likely four sentences.
-Abstract must make clear what we learn about the world because of this paper."
+    abstract: "Fast fashion is extremely profitable, accessible, and convienient, and equally -- if not more -- unethical and unsustainable.
+To illustrates the severity of fast fashion companies' rate of overproduction, this paper scrapes a representative company's online inventory at multiple points in time and finds that old products are being retired and new products added at unbelievably fast rates: too fast to be ethically possible.
+Secondary research explores this industry's cultural origins and catalysts and its serious negative ethical and environment consequences.
+Possible solutions are discussed, and the paper concludes on calling for urgent awareness and action to combat fast fashion."
 output: 
@@
 
-1\) broader context to motivate; 2) some detail about what the paper is about; 3) a clear gap that needs to be filled; 4) what was done; 5) what was found; 6) why it is important; 7) the structure of the paper.
-A reader should be able to read only the introduction and know what was done, why, and what was found.
+Fast fashion is the design, production, and selling of clothing in a very rapid and high volume approach.
+Companies participating in this practice churn out countless new, trendy products faster than ever at unbelievably cheap prices and even lower costs, reaping profit margins in the hundreds of millions and even billions.
+Customers are happy, finding it an accessible and affordable way to dress well and constantly update their closets.
+This situation may appear too good to be true: this is because it is.
 
-Estimand
+As Lucy Siegle's quote suggests, fast fashion does come at a cost, though it may not be obvious.
+It is made possible only by riding on the backs of unethical labor conditions and catastrophically negative effects on the environment.
+Despite these truths, many continue to support and buy from fast fashion companies, often as they do not grasp the true severity of these issues or that they feel it is not something that can be challenged.
+
+This paper delves into a case study of the fast fashion company ZAFUL.
+The population I hope to generalize the results to in this case is all fashion/apparel-focused companies that would be considered to be participating in fast-fashion.
+The estimand that I aim to approach is these companies' rate of producing new products and retiring old products.
+By documenting all available products in one of ZAFUL's given categories through web scraping and comparing the data collected on different dates over time, we see first-hand the unbelievably fast rate of production and turnover.
+The extremity of these results are further emphasized when compared to the product retention rate of a sustainable fashion company, KOTN.
+
+The paper then draws on secondary literature to convey how the illustrated severity of fast fashion companies' rapidness in production is inherently unethical and unsustainable, specifically by showcasing the negative consequences that are necessary to achieve those results.
+Consideration of the cultural origins and catalysts of the fast fashion industry are also provided.
+Then, discussion of possible solution spaces to these problems are explored, generally suggesting that fast fashion itself should be fought against.
+
+Fast fashion and its ramifications are not as widely understood as it must be for us to societally move away from it.
+It is this paper's intention to shine light on this topic and call for urgent awareness and action.
+
+The gathering of the data used for this paper was done by web scraping through the statistical programming language R @citeR and the Chrome extension Web Scraper @citeWS which were conducted on the sites zaful.com and kotn.com.
+Further...
+(package citations).
 
@@
 
-Lorem
+```{r}
+#| echo: false
+#| include: false
+# talk about data collection process and category (women's clothing only)
+# web scraper chrome extension for kotn (dynamic webpage)
+# looping through pagination for zaful 
+# head of both stores
+# summarize total number of products seen before and after for two stores 
+```
 
@@
 
-Lorem
+```{r}
+#| echo: false
+#| include: false
+# semi_join(before, after) to see what is the same
+# use anti_join(before, after) to see what has been removed
+# anti_join(after, before) to see what has been added
+# make a table with those 3 values 
+# make pi-chart with values proportionate to total number of products
+# make point/line graph showing increase of new products and decrease of old products
+# bar graph showing how much changed in store 1 vs store 2
+
+#z_products <- read_csv(here::here("inputs/data/zafulapril2.csv"), show_col_types = FALSE)
+
+#z_products2 <- read_csv(here::here("inputs/data/zafulapril4.csv"), show_col_types = FALSE)
+
+#k_products <- read_csv(here::here("inputs/data/kotnapril2.csv"), show_col_types = FALSE)
+
+#k_products2 <- read_csv(here::here("inputs/data/kotnapril4.csv"), show_col_types = FALSE)
+
+#samek <- semi_join(k_products, k_products2)
+#removedk <- anti_join(k_products, k_products2)
+#addedk <- anti_join(k_products2, k_products)
+
+#samez <- semi_join(z_products, z_products2)
+#removedz <- anti_join(z_products, z_products2)
+#addedz <- anti_join(z_products2, z_products)
+
+```
 

### 2023-04-04 scripts/02-gather_data.R
Rewrite data to new file location

@@ -6,7 +6,6 @@
 # Prerequisites: Use Web Scraper chrome extension for scraping KOTN data
 
 # Set up
-library(xml2)
 library(rvest)   
 library(tidyverse)
 library(dplyr)
@@ -43,14 +42,14 @@ for(page_result in seq(from = 1, to = 122, by = 1)) {
 }
 
 #Write csv of product list
-write_csv(z_products, "inputs/zafulapril2.csv")
+write_csv(z_products, "inputs/data/zafulapril2.csv")
 
 ## Second date
 #Create empty data frame
 z_products2 <- data.frame()
 
 #Loop through all product pages (sequence max set by what is seen on site) 
-for(page_result in seq(from = 1, to = 122, by = 1)) {
+for(page_result in seq(from = 1, to = 123, by = 1)) {
   url = paste0("https://www.zaful.com/clothes-e_1/g_", 
                page_result, ".html")
   raw_page <- GET(url, add_headers(headers))
@@ -67,4 +66,4 @@ for(page_result in seq(from = 1, to = 122, by = 1)) {
 }
 
 #Write csv of product list
-write_csv(z_products2, "inputs/zafulaprilXX.csv")
+write_csv(z_products2, "inputs/data/zafulapril4.csv")

### 2023-04-21 scripts/00-simulate.R
renaming of simulation data folder

@@ -46,8 +46,8 @@ store2date1
 store2date2
 
 # Download simulated data
-write_csv(store1date1, "inputs/0-simulation/store1date1.csv")
-write_csv(store1date2, "inputs/0-simulation/store1date2.csv")
+write_csv(store1date1, "inputs/simulation/store1date1.csv")
+write_csv(store1date2, "inputs/simulation/store1date2.csv")
 
-write_csv(store2date1, "inputs/0-simulation/store2date1.csv")
-write_csv(store2date2, "inputs/0-simulation/store2date2.csv")
+write_csv(store2date1, "inputs/simulation/store2date1.csv")
+write_csv(store2date2, "inputs/simulation/store2date2.csv")

### 2023-04-21 scripts/02-gather_data.R
Gathering of april 10th data

@@ -67,3 +67,27 @@ for(page_result in seq(from = 1, to = 123, by = 1)) {
 
 #Write csv of product list
 write_csv(z_products2, "inputs/data/zafulapril4.csv")
+
+## Third date
+#Create empty data frame
+z_products3 <- data.frame()
+
+#Loop through all product pages (sequence max set by what is seen on site) 
+for(page_result in seq(from = 1, to = 125, by = 1)) {
+  url = paste0("https://www.zaful.com/clothes-e_1/g_", 
+               page_result, ".html")
+  raw_page <- GET(url, add_headers(headers))
+  html <- read_html(raw_page)
+  
+  # Scrape all product names on given page
+  products <- html %>% html_elements(".js_list_title") %>% html_text()
+  
+  # Add each page's products to data frame
+  z_products3 <- rbind(z_products3, data.frame(products=products))
+  
+  # Print page number to track progress, not necessary
+  print(paste("Page:", page_result))
+}
+
+#Write csv of product list
+write_csv(z_products3, "inputs/data/zafulapril10.csv")

### 2023-04-21 outputs/paper.qmd
Paper edits

@@
 This paper delves into a case study of the fast fashion company ZAFUL.
-The population I hope to generalize the results to in this case is all fashion/apparel-focused companies that would be considered to be participating in fast-fashion.
-The estimand that I aim to approach is these companies' rate of producing new products and retiring old products.
 By documenting all available products in one of ZAFUL's given categories through web scraping and comparing the data collected on different dates over time, we see first-hand the unbelievably fast rate of production and turnover.
@@
 
-The gathering of the data used for this paper was done by web scraping through the statistical programming language R @citeR and the Chrome extension Web Scraper @citeWS which were conducted on the sites zaful.com and kotn.com.
-Further...
-(package citations).
+The gathering of the data used for this paper was done by web scraping through the statistical programming language `R` [@citeR], the packages `rvest` [@citeVest], `httr` [@citeHTTR], and the Chrome extension *Web Scraper* [@citeWS] which were conducted on the sites zaful.com and kotn.com.
+Gathering, cleaning, and further analysis was also supported by packages `tidyverse` [@citeTidy], `dplyr` [@citeDplyr], `knitr` [@citeKnit], `kableExtra` [@citeKable], and `RColorBrewer` [@citeRColor].
 
@@
 
+talk about data collection process and category (women's clothing only)
+
+web scraper chrome extension for kotn (dynamic webpage)
+
+for looping through pagination for zaful
+
+only property we are using is product name
+
+differences/sameness were found by the exact product name so even the difference in colour or size mean they are diff products (this is a lil unfortunate)
+
+summarize total number of products seen before and after for two stores (table woahh)
+
 ```{r}
+#| label: set-up
 #| echo: false
-#| include: false
-# talk about data collection process and category (women's clothing only)
-# web scraper chrome extension for kotn (dynamic webpage)
-# looping through pagination for zaful 
-# head of both stores
-# summarize total number of products seen before and after for two stores 
+#| message: false
+#| warning: false
+
+library(dplyr)
+library(tidyverse)
+library(knitr)
+library(kableExtra)
+library(RColorBrewer)
+
+#Read in data
+z_products <- read_csv(here::here("inputs/data/zafulapril2.csv"), show_col_types = FALSE)
+z_products <- z_products[!duplicated(z_products$products),]
+
+z_products2 <- read_csv(here::here("inputs/data/zafulapril4.csv"), show_col_types = FALSE)
+z_products2 <- z_products2[!duplicated(z_products2$products),]
+
+z_products3 <- read_csv(here::here("inputs/data/zafulapril10.csv"), show_col_types = FALSE)
+z_products3 <- z_products3[!duplicated(z_products3$products),]
+
+k_products <- read_csv(here::here("inputs/data/kotnapril2.csv"), show_col_types = FALSE)
+k_products <- k_products[!duplicated(k_products$products),]
+
+k_products2 <- read_csv(here::here("inputs/data/kotnapril4.csv"), show_col_types = FALSE)
+k_products2 <- k_products2[!duplicated(k_products2$products),]
+
+k_products3 <- read_csv(here::here("inputs/data/kotnapril10.csv"), show_col_types = FALSE)
+k_products3 <- k_products3[!duplicated(k_products3$products),]
+
+```
+
+```{r}
+#| label: tbl-data
+#| tbl-cap: "Total number of Women's Clothing products by store by date"
+#| echo: false
+#| message: false
+#| warning: false
+
+# create data frame of all total products by date by store
+totals <- data.frame(
+  store = c("ZAFUL (Fast Fashion)", "KOTN (Sustainable)"),
+  apr2 = c(nrow(z_products), nrow(k_products)),
+  apr4 = c(nrow(z_products2), nrow(k_products2)),
+  apr10 = c(nrow(z_products3), nrow(k_products3))
+)
+
+# create table displaying data by the dates & store
+totals %>% 
+  knitr::kable(booktabs = T, linesep = "\\addlinespace", col.names = c("Store", "April 2", "April 4", "April 10")) %>% 
+  column_spec(1, bold = T) %>% 
+  kable_styling(latex_options = "HOLD_position")%>% 
+  kable_styling(latex_options = "striped")
+
+```
+
+```{r}
+#| label: fig-data
+#| fig-cap: "ZAFUL holds much more products overall than KOTN"
+#| echo: false
+#| message: false
+#| warning: false
+
+# create data frame of all information by date and store
+totals2 <- data.frame(
+  store = c(rep("ZAFUL (Fast Fashion)", times = 3), 
+            rep("KOTN (Sustainable)", times = 3)),
+  date = c(rep(c("April 2", "April 4", "April 10"), times = 2)),
+  products = c(nrow(z_products), nrow(z_products2), nrow(z_products3),
+               nrow(k_products), nrow(k_products2), nrow(k_products3))
+)
+
+# rename columns and values
+date = c("April 2", "April 4", "April 10")
+totals2$date <- factor(totals2$date, levels = date)
+
+# create graph of data 
+totals2 %>% 
+  ggplot(aes(x = date, y = products, fill = store)) +
+  geom_col(position = "dodge") + 
+  theme_minimal() +
+  labs(x = "Date", y = "Products", fill = "Store") + 
+  theme(text=element_text(size=11, family="serif")) + 
+  scale_fill_brewer(palette = "Set1")
+
 ```
@@
 ```{r}
+#| label: tbl-summary
+#| tbl-cap: "Breakdown of added and deprecated products by date shows severity of ZAFUL's rate of production"
 #| echo: false
-#| include: false
-# semi_join(before, after) to see what is the same
-# use anti_join(before, after) to see what has been removed
-# anti_join(after, before) to see what has been added
-# make a table with those 3 values 
-# make pi-chart with values proportionate to total number of products
-# make point/line graph showing increase of new products and decrease of old products
-# bar graph showing how much changed in store 1 vs store 2
+#| message: false
+#| warning: false
 
-#z_products <- read_csv(here::here("inputs/data/zafulapril2.csv"), show_col_types = FALSE)
+# Creating subsets of what products are same, added, and removed 
+## KOTN Apr 2 -> Apr 4
+k_same <- subset(k_products2, (products %in% k_products$products))
+k_added <- subset(k_products2, !(products %in% k_products$products))
+k_removed <- subset(k_products, !(products %in% k_products2$products))
 
-#z_products2 <- read_csv(here::here("inputs/data/zafulapril4.csv"), show_col_types = FALSE)
+## KOTN Apr 2 -> Apr 10
+k_same2 <- subset(k_products3, (products %in% k_products$products))
+k_added2 <- subset(k_products3, !(products %in% k_products$products))
+k_added2_1 <- subset(k_products3, !(products %in% k_products2$products))
+k_removed2 <- subset(k_products, !(products %in% k_products3$products))
+k_removed2_1 <- subset(k_products2, !(products %in% k_products3$products))
 
-#k_products <- read_csv(here::here("inputs/data/kotnapril2.csv"), show_col_types = FALSE)
+## ZAFUL Apr 2 -> Apr 4
+z_same <- subset(z_products2, (products %in% z_products$products))
+z_added <- subset(z_products2, !(products %in% z_products$products))
+z_removed <- subset(z_products, !(products %in% z_products2$products))
 
-#k_products2 <- read_csv(here::here("inputs/data/kotnapril4.csv"), show_col_types = FALSE)
+## ZAFUL Apr 2 -> Apr 10
+z_same2 <- subset(z_products3, (products %in% z_products$products))
+z_added2 <- subset(z_products3, !(products %in% z_products$products))
+z_added2_1 <- subset(z_products3, !(products %in% z_products2$products))
+z_removed2 <- subset(z_products, !(products %in% z_products3$products))
+z_removed2_1 <- subset(z_products2, !(products %in% z_products3$products))
 
-#samek <- semi_join(k_products, k_products2)
-#removedk <- anti_join(k_products, k_products2)
-#addedk <- anti_join(k_products2, k_products)
+#create columns for data frame 
+stores <- c("ZAFUL", "", "", "", "", "KOTN", "", "", "", "")
+statuses <- c("Total", 
+             "Added from April 2", 
+             "Deprecated from April 2", 
+             "Added from April 4", 
+             "Deprecated from April 4", 
+             "Total", 
+             "Added from April 2", 
+             "Deprecated from April 2", 
+             "Added from April 4", 
+             "Deprecated from April 4")
+april2 <- c(nrow(z_products),
+           '',
+           '',
+           '',
+           '',
+           nrow(k_products),
+           '',
+           '',
+           '',
+           '')
+april4 <- c(nrow(z_products2),
+           nrow(z_added),
+           nrow(z_removed),
+           '',
+           '',
+           nrow(k_products2),
+           nrow(k_added),
+           nrow(k_removed),
+           '',
+           '')
+april10 <- c(nrow(z_products3),
+           nrow(z_added2),
+           nrow(z_removed2),
+           nrow(z_added2_1),
+           nrow(z_removed2_1),
+           nrow(k_products3),
+           nrow(k_added2),
+           nrow(k_removed2),
+           nrow(k_added2_1),
+           nrow(k_removed2_1))
 
-#samez <- semi_join(z_products, z_products2)
-#removedz <- anti_join(z_products, z_products2)
-#addedz <- anti_join(z_products2, z_products)
+# create data frame of all added and removed data
+summary <- data.frame(
+  store = stores,
+  status = statuses,
+  apr2 = april2,
+  apr4 = april4,
+  apr10 = april10)
 
+# create kable of data frame
+summary %>% 
+   knitr::kable(booktabs = T, linesep = "\\addlinespace", col.names = c("Store", " ", "April 2", "April 4", "April 10")) %>% 
+  column_spec(1:2, bold = T) %>% 
+  kable_styling(latex_options = "HOLD_position") %>% 
+  kable_styling(latex_options = "striped")
+```
+
+```{r}
+#| label: tbl-percent
+#| tbl-cap: "ZAFUL's percentage of additions and deprecations of products"
+#| echo: false
+#| message: false
+#| warning: false
+
+inc1 <- ((nrow(z_added))/(nrow(z_products)) * 100)
+inc2 <- ((nrow(z_added2_1))/(nrow(z_products2)) * 100)
+inc3 <- ((nrow(z_added2))/(nrow(z_products)) * 100)
+
+dec1 <- ((nrow(z_removed))/(nrow(z_products)) * 100)
+dec2 <- ((nrow(z_removed2_1))/(nrow(z_products2)) * 100)
+dec3 <- ((nrow(z_removed2))/(nrow(z_products)) * 100)
+
+percent <- data.frame(
+  status = c("Increase (+%)", "Decrease (-%)"),
+  apr2to4 = c(inc1, dec1),
+  apr2to10 = c(inc2, dec2),
+  apr4to10 = c(inc3, dec3)
+)
+
+percent %>% 
+  knitr::kable(booktabs = T, linesep = "\\addlinespace", col.names = c(" ", "April 2nd to 4th", "April 4th to 10th", "April 2nd to 10th")) %>% 
+  column_spec(1, bold = T) %>% 
+  kable_styling(latex_options = "HOLD_position")%>% 
+  kable_styling(latex_options = "striped")
+```
+
+```{r}
+#| label: fig-added
+#| fig-cap: "Total num of products seem consistent, but the proportion of added ones are large"
+#| echo: false
+#| message: false
+#| warning: false
+
+dates <- c("April 2", "April 4", "April 10")
+productss <- c(nrow(z_products), 
+               (nrow(z_products2) - nrow(z_added)), 
+               (nrow(z_products3) - nrow(z_added2)), as.integer(0), 
+               nrow(z_added), 
+               nrow(z_added2))
+
+added <- data.frame(
+  date = c(rep(dates, times = 2)),
+  add = c(rep("Same from Apr 2nd", times = 3), rep("Added", times = 3)),
+  products = productss
+)
+
+date = c("April 2", "April 4", "April 10")
+added$date <- factor(totals2$date, levels = date)
+
+added %>% 
+  ggplot(aes(x = date, y = products, fill = add)) +
+  geom_col() +
+  theme_minimal() +
+  labs(x = "Date", y = "Products", fill = "Added?") + 
+  theme(text=element_text(size=11, family="serif")) + 
+  scale_fill_brewer(palette = "Set1")
 ```

### 2023-04-22 outputs/paper.qmd
Paper edits

@@
 ---
-title: "Fast Fashion's Rapid Rate of Overproduction is Observedly Unsustainable & Unethical: Why and How did we get here?"
+title: "Fast Fashion's Rapid Rate of Production is Observedly Unsustainable & Unethical: Why and How did we get here?"
 author: "Jayden Jung"
@@
     abstract: "Fast fashion is extremely profitable, accessible, and convienient, and equally -- if not more -- unethical and unsustainable.
-To illustrates the severity of fast fashion companies' rate of overproduction, this paper scrapes a representative company's online inventory at multiple points in time and finds that old products are being retired and new products added at unbelievably fast rates: too fast to be ethically possible.
+To illustrate the severity of fast fashion companies' rapid rate of production, this paper scrapes a representative company's online inventory at multiple points in time and finds that old products are being retired and new products added in big amounts and at fast speeds: too big and fast to be ethically possible.
 Secondary research explores this industry's cultural origins and catalysts and its serious negative ethical and environment consequences.
@@
 >
-> --- Lucy Siegle, Journalist and Producer of *The True Cost*, 2015.
+> --- Lucy Siegle, Journalist and Producer of *The True Cost* @citeTrueCost
 
-Fast fashion is the design, production, and selling of clothing in a very rapid and high volume approach.
+Fast fashion is the design, production, and selling of clothing in a very rapid and high volume approach [@citeGoodTrade].
 Companies participating in this practice churn out countless new, trendy products faster than ever at unbelievably cheap prices and even lower costs, reaping profit margins in the hundreds of millions and even billions.
@@
 By documenting all available products in one of ZAFUL's given categories through web scraping and comparing the data collected on different dates over time, we see first-hand the unbelievably fast rate of production and turnover.
-The extremity of these results are further emphasized when compared to the product retention rate of a sustainable fashion company, KOTN.
+In one case, in about 1 week, ZAFUL added over 2,500 women's clothing products to their website, nearly a 35% increase (See @tbl-summary & @tbl-percent).
+The extremity of these results are further emphasized when compared to the product retention rate of a sustainable fashion company, KOTN, that, during the period of this paper's observation, did not add or remove any products.
 
@@
 
-talk about data collection process and category (women's clothing only)
+All data collected and used for this paper was proccurred through web scraping.
+Two e-commerce websites were chosen for this: ZAFUL (zaful.com), a fast fashion company, and KOTN (kotn.com), a sustainable, slow fashion company.
+For both, I restricted the collection to only the Women's Clothing category for better direct comparison and feasibility.
+Scraping of ZAFUL's products was conducted through `R` [@citeR], where the packages `rvest` [@citeVest] and `httr` [@citeHTTR] allowed me to loop through the pagination division of the products.
+To scrape for KOTN's products, I used the *Web Scraper* Chrome extension [@citeWS], which enabled me to work around the dynamic nature of this site loading in new products as you scroll.
 
-web scraper chrome extension for kotn (dynamic webpage)
-
-for looping through pagination for zaful
-
-only property we are using is product name
-
-differences/sameness were found by the exact product name so even the difference in colour or size mean they are diff products (this is a lil unfortunate)
-
-summarize total number of products seen before and after for two stores (table woahh)
+The only variable I collected was every product's exact name.
+This would enable me to compare the total list on different dates to identify the added and removed products.
+To accomplish this comparison, the scraping was conducted for both stores on three separate dates: April 2nd, April 4th, and April 10th.
+The resulting six data sets each only had the `products` property of a character class that held all the scraped product names from that store on that day.
+@tbl-head provides a preview of these data sets.
 
@@
 library(RColorBrewer)
+knitr::opts_chunk$set(fig.pos = "H")
 
@@
 ```{r}
+#| label: tbl-head
+#| tbl-cap: "Preview of ZAFUL and KOTN products from April 2nd"
+#| echo: false
+#| message: false
+#| warning: false
+
+z_head <- head(z_products)
+k_head <- head(k_products)
+
+z_head %>% 
+  knitr::kable(booktabs = T, linesep = "\\addlinespace", col.names = c("ZAFUL Products")) %>% 
+  kable_styling(latex_options = "striped") %>% 
+  kable_styling(latex_options = "HOLD_position")
+
+k_head %>% 
+  knitr::kable(booktabs = T, linesep = "\\addlinespace", col.names = c("KOTN Products")) %>% 
+  kable_styling(latex_options = "striped") %>% 
+  kable_styling(latex_options = "HOLD_position")
+```
+
+\pagebreak
+
+One limitation of this was that, for ZAFUL's products, this would indicate that two products of the same name but differing colours or sizes would register as different products, while KOTN's wouldn't, entirely due to a difference in how the products were displayed on the respective sites.
+This was allowed, as the addition of more sizes and colours does require production efforts, but the analysis below was not adjusted to account for it.
+Another issue was that ZAFUL had some cases of duplicate product names showing up on different pages; the final data sets were cleaned to filter out any of these cases.
+
+@tbl-data summarizes the total number of recorded products for both stores on the three dates that they were recorded: April 2nd, April 4th, and April 10th, 2023.
+This table, coupled with @fig-data, reveals the sheer volume of ZAFUL's quantity of products compared to KOTN; ZAFUL approximates 7,300-7,500 products, while KOTN at 248.
+ZAFUL's Women's Clothing section has nearly thirty times as many products as KOTN's.
+Aside from this, though, these initial impressions do not reveal much.
+KOTN seems to have no fluctuation in product volume, while ZAFUL's seems to remain around similar values.
+
+```{r}
 #| label: tbl-data
@@
   column_spec(1, bold = T) %>% 
-  kable_styling(latex_options = "HOLD_position")%>% 
-  kable_styling(latex_options = "striped")
+  kable_styling(latex_options = "striped") %>% 
+  kable_styling(latex_options = "HOLD_position")
 
@@
 
+\pagebreak
+
 # Results
+
+By comparing what character entries are in a latter data set and not the former, and what is in the former but not the latter, I was able to infer which products were newly added and which had been deprecated between the date ranges of the web scraping.
+@tbl-summary conveys this.
+This approach reveals much more information than the raw quantity of products at each date.
+Despite ZAFUL's total product quantity only changing by a relatively little amount, the actual number of products that are added and removed are much larger.
+From the 2nd to the 4th, there were only 80 more products overall, but that was the result of 1642 products being removed and 1702 products added.
+From 2nd to the 4th, there were 180 more products, but it is broken down into 2364 removed and 2544 added.
+Contrarily, KOTN's 248 products remain unchanged both in total quantity and exact composition over the entire time.
 
@@
 
+@tbl-percent shows the percentage of the added and deprecated products between the three given date ranges (April 2-4, 4-10, and 2-10).
+This provides a clearer image of how large these values are on a relative level.
+From April 2nd to 4th, the added items were equivalent to 23% of the quantity of original products, nearly a quarter, which had been replaced in two days.
+April 2nd to 10th, the added items were equivalent to nearly 35% of the number of original ones, and the decreased items over 32%.
+This means that over a third of the 7319 products were replaced in eight days.
+This is illustrated also in @fig-added, where, within each total quantity of products by date, the added quantity is highlighted.
+
 ```{r}
@@
 
-Lorem
+This case of ZAFUL's observed rate of rapidly deprecating old products and adding new products in the span of just a few days or a week is a small snapshot of the fast fashion industry.
+It provides a practical illustration of how fast this industry operates.
+Today, the classic four-season-a-year model of fashion collections is a thing of the far past, and most major companies are producing at 52 "micro-seasons" per year, a new collection every week, or more, even thousands new items in a couple of days as we've seen in ZAFUL's case [@citeGoodTrade].
+
+The world, today, consumes around 80 billion new pieces of clothing every year, 400% more than we did 20 years ago [@citeTrueCost].
+The sheer amount of clothing that is produced, at the speed that it is, brings up the question of why it happens and how it is even possible.
+These two questions are explored below.
 
@@
 
-Lorem
+Clothing, until the 1900s, was mostly made at home or specifically by individual experts: then, industrialization led to the popularization of factory-made clothes, which was both cheaper and more convenient [@citeOverdressed].
+Following World War II, Americans procured began to actively follow fashion trends.
+In the 1970s, commercialization of clothes developed furthered, and department stores with even more inexpensive options became normalized.
+The concepts of a "good deal" and shopping around sales schedules originated from this period.
+
+The 1990s and 2000s marked the rise of fast fashion due to fierce competition between companies to outperform each other; frontliners like GAP, H&M, and Zara pioneered new ways of producing clothes at extremely fast speeds to actively meet ongoing fashion trends and stand out as the trendiest option to consumers [@citeOverdressed].
+By forgoing quality, these companies were able to do this at the cheapest possible costs, and began earning record-high profit margins.
+Despite these clothes being cheaper per item for the consumer as well, it led them to shopping for more clothes more frequently, leading to more spending overall and higher revenue for the companies.
+This financial incentive drove companies to further actively embed fast fashion into culture, leading to a feedback loop of even more invested consumers expecting even faster turnaround of the most recent trends.
+
+Recent surveys find that a majority of teenagers (over 60%) buy clothes that they never wear, and even more that only wear it once, attributing it to the pressure they feel to stay trendy and not be seen wearing the same thing multiple times [@citeGiveUp].
 
@@
 
-Lorem
+The fast fashion industry has extreme ethical and environmental consequences.
+To match the demands of fast fashion companies' requirement for lead time and production speed, the labourers at the lowest tiers suffer greatly.
+Many work endless hours in unsafe, inhumane conditions, with unlivable salaries [@citeTrueCost].
+Bangladeshi garment workers are beaten by their employers if they do not meet quotas, and some Cambodian ones have been shot by the police for protesting the working conditions [@citeTrueCost].
+This industry also depends on the use of child labourers.
+Some consumers of major brands like SHEIN and ZARA have reported seeing pleading messages like "HELP" being written onto their clothes, presumably by such workers [@citeGiveUp].
 
-## Defining Solution Spaces
+The garment industry is a major driver of pollution and climate change.
+Garment production currently produces 92 million tonnes of waste and uses up 79 trillion litres of water every year, and produces 10% of the world's CO2 emissions [@citeEnvPrice].
+Beyond production, 85% of textiles go to the dump [@citeEnvImpact].
+Of the clothing that does get donated, only 20% is actually resold, and the rest are also dumped [@citeTrueCost].
 
-Lorem
+## Stepping towards a Solution by Better Understanding that one is needed
+
+A major blockade to pursuing solutions to the issues resulting from fast fashion is that there is still a major lack of social consciousness around the topic.
+This paper, in exploring the specific case of ZAFUL's rate of production and communicating impressionable, ridiculous statistics on its scale, is one example of what an intermediary step to accommodate this should look like: spreading practical awareness and sparking a degree of outrage.
+
+Despite younger generations like Gen Z reportedly advocating against fast fashion and in favor of sustainability when the topics are discussed directly [@citeGiveUp] [@citeFallApart], as mentioned before, their actions do not reflect these sentiments, as they continue to purchase from fast fashion brands without feeling conscious guilt.
+There is a feeling of disconnect between individual choice and real, macro-level consequences of fast fashion.
+There are also some defenders of such actions that claim that fast fashion is the only affordable and accessible option for some [@citeGiveUp].
+
+Making the alternative, sustainable, slow fashion, as seen in companies like KOTN could very much help with this issue [@citeFallApart].
+But it must be done in tandem with aggressive moralization of fast fashion as an undeniably unethical, unsustainable, wrong thing to partake in.
 
@@
 
-Lorem
+A larger scale, more robust approach taken to this paper's attempt to document the rate of production of fast fashion companies could be conducted to better accomplish the goal of inciting public concern for the current state of this industry.
+Though some information exists and ball-park guesses can be made, there is currently no reliable source of exactly how much harm each of these fast fashion companies are causing.
+Without a tangible point of wrongness, it is difficult for individuals to find reason with changing the status quo.
+Beyond that, better exploration and public understanding of what actions individuals can take to fight against fast fashion would likely help people redirect their helplessness.
 
@@
 
-Lorem
+Other than the shortcomings addressed throughout the paper, this project generally operated on a very limited scale, only showing snippets of a single company's actions over a time span of barely over a week.
+Though this may be seen as a limitation in one regard due to the absolute lack of actual generalizableness, I ask that it is also thought of as a calling to reveal more.
+If a paper done at such a small scale shows as shocking of results as it has, then one conducted robustly must reveal even more criminalizing results of the industry.
 
